Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-03 manuscript.tex
Cite truth shape model and correct equation ref

In this section, we demonstrate the use of the incremental shape reconstruction algorithm with asteroids 1620 Geographos and 6489 Golevka.
\todo{ add references to the true shape model we are using}.
Their properties are listed at \Cref{tab:kinematic_asteroids}.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}

@@

Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
\todo{ resolve the undefined reference to eq:potential}
The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

>>>>

In this section, we demonstrate the use of the incremental shape reconstruction algorithm with asteroids 1620 Geographos and 6489 Golevka.
Their properties are listed at \Cref{tab:kinematic_asteroids}.
Truth shape models for Geographos adn Golevka are computed based on Earth based radar measurements~\cite{neese2004}.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}

@@

Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
The computational cost of the polyhedron potential model, given by~\cref{eq:attraction}, is roughly proportional to the number of faces in the shape model.
As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
